\documentclass{article}
\usepackage[utf8]{inputenc}

\title{HW 6}
\author{Team Bingo}
\date{March 2020}

\begin{document}

\maketitle

\section{Persistance}

\subsection{Data Model}
Our data is mapped directly by Django's Object Relational Mapper. See models.py
for details. 

\subsection{Queries}
Filtering of colleges and user profiles is almost done exclusively through
django's QuerySet api. The only exception is when lax filtering is specified,
application code is required to fetch objects whose the filters are not
reported. See search in views.py for details

\section{Code Convention}

\subsection{Python Backend}
Adhere to PEP8: https://www.python.org/dev/peps/pep-0008/ \\ 
Style enforcing using Black: https://github.com/psf/black


\subsection{JavaScript Frontend}
Adhere to prettier: https://prettier.io/docs/en/index.html


\section{Implementation Status Report}
See gradingsheet.xlsx 

\section{Installation Manual}
See README in source code directory

\section{Test Report}
\subsection{Unit Tests}
Series of tests for backend functions login, register, and search.
A set of unit tests to test scraping college rankings, data, scorecard, and
niche.com. 

\subsection{Integration Tests}
Use a web browser automation tool, selenium, to test integration of frontend and
backend. We test search, login, and register.

\section{Contribution}
Omar - backend 
Olesia, Jafree, Bing: design, frontend, presentation

\section{Data}
See backend/data.

\section{Design}
See backend/design for diagrams and attached documents

\end{document}

