\documentclass{article}
\usepackage[utf8]{inputenc}

\title{HW 7}
\author{Team Bingo}
\date{April 2020}

\begin{document}

\maketitle

\section{Concurrency}
As Professor Stoller has mentioned, the project has relatively few concurrency
issues. There might be small race conditions between an administrator and a
student such as marking a decision as questionable, but these are minor. In
addition users can only edit their own profile. The only shared data that is
accessible by two or more students is High School. When a hs is not in the system, it has to
be scraped. This can happen in two cases, when a user is searching for similar
high schools, or when he or she updates his or her profile. 

The way we handle this is by using atomic transactions in get-similar-hs and
post-student-profile in views.py. We choose the appropriate transaction
boundaries and make sure the transaction is atomic, thus preventing any
concurrency issues.


\section{Implementation Status Report}
See gradingsheet.xlsx 

\section{Installation Manual}
See README in source code directory

\section{Test Report}

\begin{verbatim}
https://docs.google.com/document/d/1Xa17dZhbSP-B_YK-8fXd25HYCkJckMbbPTcGqfWtX4o/edit?usp=sharing
\end{verbatim}


\subsection{Unit Tests}
Series of tests for backend functions login, register, and search.
A set of unit tests to test scraping college rankings, data, scorecard, and
niche.com. 

\subsection{Integration Tests}
Use a web browser automation tool, selenium, to test integration of frontend and
backend. We test search, login, and register.

\section{Contribution}
Omar - backend 
Olesia, Jafree, Bing: design, frontend, presentation

\section{Code}
See backend and frontend files.

\section{Data}
See backend/data.

\section{Requirements}
See /design for requirement document. 

\section{Design}
See /design for diagrams and attached documents.

\section{Video}
\begin{verbatim}
https://drive.google.com/file/d/17t2HHd2OvOH7eIR3I12Z2X6RGqk0K8n_/view?usp=sharing
\end{verbatim}
\end{document}

